**Almond Industry IPM + Ecoinformatics**
--------------------------------------------------------------------------------

************
If at any point you would like to see some of the data in more detail
let me know and I'll try to quickly make a plot for you


************

## The Datasets:

### **dmg** - nut damage.

```{r, echo = FALSE}
load("pred_analysis2_6_15.rda")
```
**dmg** has dimensions:
```{r, echo = FALSE}
dim(dmg)
```
But I am mainly interested in columns:
```{r, echo = FALSE}
colnames(dmg[, c(1:12, 16, 64, 72)])
```


### **p.n** - pesticide and mating distruption use.

**p.n** has dimensions:

```{r, echo = FALSE}
dim(p.n)
```
with data on:
```{r, echo = FALSE}
colnames(p.n)
```
*NOTE*:
```{r}
summary(as.factor(as.character(p.n$Target.Pest)))
```

We are only interested (at the moment) in Navel Orangeworms. **p.n** is acutally
only a small subset of a MUCH larger dataset **p** which contains pesticide use
data targeting far more species. 

### **c** - insect densities.

This is really the honey pot of our analysis.
**c** has dimension:
```{r, echo = FALSE}
dim(c)
```
with data on:
```{r, echo = FALSE}
colnames(c)
```

## Question \#1: Can we assess pesticide efficacy?

```{r, warning = FALSE}
library(ggplot2)
library(wesanderson)
ggplot(c, aes(x = DayOfYear, y = Females, colour = TrapType)) +
geom_point(size = 2) + facet_wrap(~Ranch) +
scale_color_manual(values = wes_palette("Darjeeling"))
```
