---
output:
  ioslides_presentation:
    widescreen: true
    smaller: false
---


# Almond Industry IPM + Ecoinformatics {.flexbox .vcenter}


# What Datasets have we got? {.flexbox .vcenter}


## dmg

```{r, echo = FALSE}
load("../pred_analysis2_11_15.rda")
```
**dmg** has dimensions:
```{r, echo = FALSE}
dim(dmg)
```
But I am mainly interested in columns:
```{r, echo = FALSE}
colnames(dmg[, c(1:12, 16, 64, 72)])
```


## p.n

**p.n** has dimensions:

```{r, echo = FALSE}
dim(p.n)
```
with data on:
```{r, echo = FALSE}
colnames(p.n)
```

## Navel Orangeworms
For the moment we are only interested in Navel Orangeworms. **p.n** is acutally
only a small subset of a MUCH larger dataset **p** which contains data on pesticide
targeting far more species. 


## **c** | insect densities.

**c** has dimension:
```{r, echo = FALSE}
dim(c)
```
with data on:
```{r, echo = FALSE}
colnames(c)
```

# Let's take a look at general patterns in seasonal NOW density:

----

```{r, warning = FALSE, echo = FALSE, fig.width = 11, fig.height = 6}
library(ggplot2)
library(wesanderson)
temp <- c
temp$TrapType <- as.character(temp$TrapType)
ggplot(subset(temp, !is.na(Males)),
		    aes(x = DayOfYear, y = Males, colour = TrapType)) +
		    geom_point(size = 2) + 	  
		    scale_color_manual(values = wes_palette("Darjeeling"))
```

----

```{r, warning = FALSE, echo = FALSE, fig.width = 11, fig.height = 6}
library(ggplot2)
library(wesanderson)
temp <- c
temp$TrapType <- as.character(temp$TrapType)
ggplot(subset(temp, !is.na(Females)),
		    aes(x = DayOfYear, y = Females, colour = TrapType)) +
		    geom_point(size = 2) + 	  
		    scale_color_manual(values = wes_palette("Darjeeling"))
```

----

```{r, warning = FALSE, echo = FALSE, fig.width = 11, fig.height = 6}
library(ggplot2)
library(wesanderson)
temp <- c
temp$TrapType <- as.character(temp$TrapType)
ggplot(subset(temp, !is.na(Eggs)),
		    aes(x = DayOfYear, y = Eggs, colour = TrapType)) +
		    geom_point(size = 2) + 	  
		    scale_color_manual(values = wes_palette("Darjeeling"))
```


# First Question: can we assess pesticide efficacy? 



----

```{r, warning = FALSE, echo = FALSE, fig.width = 10, fig.height = 7}
c_conv <- subset(c,Trtmnt %in% c("Conv","Control"))
temp1 <- merge( p.n.by.block, c_conv, by = c("Ranch", "Block", "Year"))

pal <- wes_palette("Darjeeling", 6, type = "continuous")

ggplot(temp1, aes(x = DayOfYear.y, y = Males, group = Site.y)) +
    scale_color_manual(values = pal) +
    geom_point(size=2) +
    geom_vline(aes(xintercept = DayOfYear.x,
                   colour = Product..Agrian.,
                   linetype = "longdash")) +
    facet_wrap(~Site.y)
```
